---
title: 'Dashboard'
output: 
  flexdashboard::flex_dashboard:
    logo: www/logo.svg.png
    theme : spacelab

runtime: shiny_prerendered

---


  
<style>

img {
  max-width: 69px;
  max-height: 50px;
}

.navbar-logo {
  margin-top: 6px;
}

.navbar-logo img {
  margin-right: 34px;
}

.irs--shiny .irs-bar {
    top: 25px;
    height: 7px;
    border-top: 7px solid #c0f12d;
    border-bottom: 2px solid #428bca;
    background: #1d31bd;
}

.selectize-input {
  border: 2px solid #cfff02;
  padding: 8px 11px;
  display: inline-table;
  width: 87%;
  overflow: hidden;
  position: relative;
  z-index: 1;
  box-sizing: border-box;
  box-shadow: none;
  border-radius: 25px;
}


body {
  background: #ffffff;
    padding: 50px 0 0 8px;
  font-family: "Source Sans Pro",Calibri,Candara,Arial,sans-serif;
  font-size: 14px;
  line-height: 2;
  color: #3522c5;
}

.section.sidebar {
  position: absolute;
  top: 80px;
  left: 9px;
  right: -15px;
  bottom: 0;
  border-right: 10px solid #f2ff86;
  background-color: white;
  padding-left: 28px;
  padding-right: 2px;
  visibility: hidden;
  overflow: initial;
}

.irs--shiny.irs-with-grid {
    height: 61px;
    width: 162px;
}

.form-group {
    margin-bottom: 4px;
}
</style>

```{r setup, include=FALSE}

library(tidyverse)
library(readxl)
library(highcharter)
library(flexdashboard)
library(dplyr)

#suppressPackageStartupMessages(library(dplyr))
# packageVersion('dplyr')

```


```{r data, include=FALSE}

data = read.csv('data/poke.csv')


colnames(pokemon)[colnames(pokemon) == "pokemon"] = "name"


habilidades = sort(names(data[,c(20, 23, 26, 29, 34, 35, 36, 39)]))


df = left_join(data, select(pokemon, c('name','image_url', 'type_1', 'type_2', 'type_1_color', 'type_2_color')), by ='name') %>%
  mutate(type2 = ifelse(type2 == '', type1, type2))


df$type_2_color = ifelse(is.na(df$type_2_color), df$type_1_color, df$type_2_color)


pkmn_min <- df |> 
  select(type_1, type_2, type_1_color) |>
  mutate(type_1 = stringr::str_to_title(type_1)) |> 
  mutate(type_2 = ifelse(is.na(type_2), type_1, paste(type_1, "-", type_2))) |>
  mutate(val = 1)

cols <- pkmn_min |> 
  count(type_1, type_2, type_1_color, sort = TRUE) |> 
  pull(type_1_color) |> 
  unique()


group = df %>% 
  group_by(type1, type2) %>% 
  count()
  


function_types = function(df) {
  
  lista_final = list()
  for (i in 1:nrow(df)){
    lista_final[[i]] = list(from = as.character(df[i,][1]) ,
                          to = as.character(df[i,][2]) ,
                          weight = as.numeric(df[i,][3] ))
  }
  
  if (length(lista_final) == nrow(df)){
    return(lista_final)
  }
  else{
    return(NULL)
  }
  
}

types_dependency = function_types(group)

 
```




```{r}

highchart() %>%
    hc_chart(type = 'dependencywheel') %>%
    hc_add_series(
      data = types_dependency,
       dataLabels = list(
        color = '#333',
        textPath = list(
          enabled = TRUE
        )
    ),
    distance = 10,
    size = '95%') %>%  

    hc_title(text = paste0('Pokemon Dependency Wheel Plot'),
       style = list(fontSize = '20px', fontWeight = 'bold')) %>% 
    hc_credits(enabled = TRUE, 
               text = "Fuente: Kaggle",
               align = "right",
               verticalAlign = "bottom",
        style = list(color = "black", 
                     fontSize = '12px'),
        href = "https://www.kaggle.com/datasets/rounakbanik/pokemon") %>% 
    hc_yAxis(labels = list(style = list(color = "black")),
             tickColor = "black") %>% 
    hc_xAxis(labels = list(style = list(color = "black")),
             tickColor = "black") %>% 
  highcharter::hc_caption(
    text = "Dependency Wheel Plot using Pokemon Data", 
    useHTML = TRUE
    )


```

